Defficiency Screen Functional Analysis

### 2023-07-17 TKT_RNAseq/R Code/GO_Analysis.Rmd
update

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/TKT_RNAseq/CountTables/"
cpmdata = read.csv(paste0(git.dir,"TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg.names = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv", row.names = 1)
kegg = readRDS("/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/kegg.symbol2path.RData")

##i=1
##kegg.names=unique(substr(kegg,6,13))
##names(kegg.names)=as.vector(kegg.names)
##while(i<=length(kegg.names)){
##  kegg.names[i] <- strsplit(keggGet(kegg.names[i])[[1]]$NAME," - ")[[1]][1]
##  i=i+1
##}

##write.csv(kegg.names, "/Users/johncsantiago/Documents/GitHub/WhartonLab/Deficiency Screen/DataFiles/KEGG.names.csv")

keggID=keggConv("dme","ncbi-geneid")

```{r include=F, echo=F}

sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
                           "Symbol"]
genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxDf.GO = GO.wall
write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")

##KEGG term enrichment is KEGG
KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxDf.KEGG = KEGG
write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")

sigs = GeneIDKey[row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05], "Symbol"]
sigs = GeneIDKey[intersect(row.names(TKT.EdgeR)[TKT.EdgeR$GRF.CxDf <= .05],
                           row.names(cpmdata)[apply(cpmdata[,c("GR.F1","GR.F2","TktDfGR.F1","TktDfGR.F2","TktDfGR.F3")], 1, min) >5]), 
                           "Symbol"]
genes = setNames(rep(0, nrow(TKT.EdgeR)), GeneIDKey[row.names(TKT.EdgeR), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxDf.GO = GO.wall
write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq//DataFiles/GRF.CxDf.GOAnalysis.csv")

##KEGG term enrichment is KEGG
KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxDf.KEGG = KEGG
write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")

GO.data = GRF.CxDf.GO
GO.data = GO.data[GO.data$ontology == 'BP',
                  c("category", "term","adjp", "numDEInCat", "numInCat")]

>>>>

```{r echo = F, include =F}
##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

##keggID=keggConv("dme","ncbi-geneid")

datadir = "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/"

GRF.CxDf.GO  = read.csv(paste0(datadir, "GRF.CxDf.GOAnalysis.csv"), row.names =1)
GRF.CxOE.GO  = read.csv(paste0(datadir, "GRF.CxOE.GOAnalysis.csv"), row.names =1)
WTF.CxDf.GO  = read.csv(paste0(datadir, "WTF.CxDf.GOAnalysis.csv"), row.names =1)
WTF.CxOE.GO  = read.csv(paste0(datadir, "WTF.CxOE.GOAnalysis.csv"), row.names =1)

GRM.CxDf.GO  = read.csv(paste0(datadir, "GRM.CxDf.GOAnalysis.csv"), row.names =1)
GRM.CxOE.GO  = read.csv(paste0(datadir, "GRM.CxOE.GOAnalysis.csv"), row.names =1)
WTM.CxDf.GO  = read.csv(paste0(datadir, "WTM.CxDf.GOAnalysis.csv"), row.names =1)
WTM.CxOE.GO  = read.csv(paste0(datadir, "WTM.CxOE.GOAnalysis.csv"), row.names =1)

GR.FxM.GO    = read.csv(paste0(datadir, "GR.FxM.GOAnalysis.csv"), row.names =1)
WT.FxM.GO    = read.csv(paste0(datadir, "WT.FxM.GOAnalysis.csv"), row.names =1)

GRxWT.FC.GO  = read.csv(paste0(datadir, "GRxWT.FC.GOAnalysis.csv"), row.names =1)
GRxWT.FDf.GO = read.csv(paste0(datadir, "GRxWT.FDf.GOAnalysis.csv"), row.names =1)
GRxWT.FOE.GO = read.csv(paste0(datadir, "GRxWT.FOE.GOAnalysis.csv"), row.names =1)

GRxWT.MC.GO  = read.csv(paste0(datadir, "GRxWT.MC.GOAnalysis.csv"), row.names =1)
GRxWT.MDf.GO = read.csv(paste0(datadir, "GRxWT.MDf.GOAnalysis.csv"), row.names =1)
GRxWT.MOE.GO = read.csv(paste0(datadir, "GRxWT.MOE.GOAnalysis.csv"), row.names =1)

SigDEGs = TKT.EdgeR
SigDEGs[,] = 0

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktDfGR.F"],1,min) > 5)], "GRF.CxDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktOEGR.F"],1,min) > 5)], "GRF.CxOE"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "WTF.CxDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "WTF.CxOE"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FC <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "WT.F"],1,min) > 5)], "GRxWT.FC"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "GRxWT.FDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "WTF.CxOE"] =1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktDfGR.M"],1,min) > 5)], "GRM.CxDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktOEGR.M"],1,min) > 5)], "GRM.CxOE"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "WTM.CxDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "WTM.CxOE"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MC <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "WT.F"],1,min) > 5)], "GRxWT.MC"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "GRxWT.MDf"] = 1

SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "GRxWT.MOE"] = 1
SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$GR.FxM  <= .05)], "GR.FxM"] = 1
SigDEGs[row.names(TKT.EdgeR)[(TKT.EdgeR$WT.FxM  <= .05)], "WT.FxM"] = 1
```

##GOterm and KEGG enrichment analysis for all EdgeR comparisons
##```{r include=F, echo=F}

##############
## GRF.CxDf ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktDfGR.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxDf.GO = GO.wall
write.csv(GRF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxDf.KEGG = KEGG
write.csv(GRF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxDf.KEGGAnalysis.csv")

##############
## GRF.CxOE ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "TktOEGR.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRF.CxOE.GO = GO.wall
write.csv(GRF.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRF.CxOE.KEGG = KEGG
write.csv(GRF.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRF.CxOE.KEGGAnalysis.csv")

##############
## WTF.CxDf ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
WTF.CxDf.GO = GO.wall
write.csv(WTF.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
WTF.CxDf.KEGG = KEGG
write.csv(WTF.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxDf.KEGGAnalysis.csv")

##############
## WTF.CxOE ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTF.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
WTF.CxOE.GO = GO.wall
write.csv(WTF.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
WTF.CxOE.KEGG = KEGG
write.csv(WTF.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTF.CxOE.KEGGAnalysis.csv")

##############
## GRM.CxDf ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktDfGR.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRM.CxDf.GO = GO.wall
write.csv(GRM.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRM.CxDf.KEGG = KEGG
write.csv(GRM.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxDf.KEGGAnalysis.csv")

##############
## GRM.CxOE ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "TktOEGR.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRM.CxOE.GO = GO.wall
write.csv(GRM.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRM.CxOE.KEGG = KEGG
write.csv(GRM.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRM.CxOE.KEGGAnalysis.csv")

##############
## WTM.CxDf ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxDf <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
WTM.CxDf.GO = GO.wall
write.csv(WTM.CxDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
WTM.CxDf.KEGG = KEGG
write.csv(WTM.CxDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxDf.KEGGAnalysis.csv")

##############
## WTM.CxOE ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WTM.CxOE <= .05) & (apply(cpmdata[,groups$Group == "WT.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
WTM.CxOE.GO = GO.wall
write.csv(WTM.CxOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
WTM.CxOE.KEGG = KEGG
write.csv(WTM.CxOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WTM.CxOE.KEGGAnalysis.csv")

##############
## GRxWT.FC ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FC <= .05) & (apply(cpmdata[,groups$Group == "GR.F" | groups$Group == "WT.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.FC.GO = GO.wall
write.csv(GRxWT.FC.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FC.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.FC.KEGG = KEGG
write.csv(GRxWT.FC.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FC.KEGGAnalysis.csv")

###############
## GRxWT.FDf ##
###############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FDf <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.F" | groups$Group == "TktDfWT.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.FDf.GO = GO.wall
write.csv(GRxWT.FDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.FDf.KEGG = KEGG
write.csv(GRxWT.FDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FDf.KEGGAnalysis.csv")

###############
## GRxWT.FOE ##
###############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.FOE <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.F" | groups$Group == "TktOEWT.F"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.FOE.GO = GO.wall
write.csv(GRxWT.FOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.FOE.KEGG = KEGG
write.csv(GRxWT.FOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.FOE.KEGGAnalysis.csv")

##############
## GRxWT.MC ##
##############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MC <= .05) & (apply(cpmdata[,groups$Group == "GR.M" | groups$Group == "WT.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.MC.GO = GO.wall
write.csv(GRxWT.MC.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MC.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.MC.KEGG = KEGG
write.csv(GRxWT.MC.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MC.KEGGAnalysis.csv")

###############
## GRxWT.MDf ##
###############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MDf  <= .05) & (apply(cpmdata[,groups$Group == "TktDfGR.M" | groups$Group == "TktDfWT.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.MDf.GO = GO.wall
write.csv(GRxWT.MDf.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MDf.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.MDf.KEGG = KEGG
write.csv(GRxWT.MDf.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MDf.KEGGAnalysis.csv")

###############
## GRxWT.MOE ##
###############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GRxWT.MOE  <= .05) & (apply(cpmdata[,groups$Group == "TktOEGR.M" | groups$Group == "TktOEWT.M"],1,min) > 5)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GRxWT.MOE.GO = GO.wall
write.csv(GRxWT.MOE.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MOE.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GRxWT.MOE.KEGG = KEGG
write.csv(GRxWT.MOE.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GRxWT.MOE.KEGGAnalysis.csv")

############
## GR.FxM ##
############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$GR.FxM  <= .05)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
GR.FxM.GO = GO.wall
write.csv(GR.FxM.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GR.FxM.GOAnalysis.csv")

KEGG=goseq(pwf,gene2cat=kegg)
KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
KEGG$Name=kegg.names[row.names(KEGG),1]
GR.FxM.KEGG = KEGG
write.csv(GR.FxM.KEGG, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/GR.FxM.KEGGAnalysis.csv")

############
## WT.FxM ##
############
sigs = GeneIDKey[row.names(TKT.EdgeR)[(TKT.EdgeR$WT.FxM  <= .05)], "Symbol"]
genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
genes[sigs] = 1
pwf=nullp(genes,"dm3","geneSymbol")
GO.wall=goseq(pwf,"dm3","geneSymbol")
GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
row.names(GO.wall) = GO.wall$category
WT.FxM.GO = GO.wall
write.csv(WT.FxM.GO, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/DataFiles/WT.FxM.GOAnalysis.csv")
